---
title: "Kristin's SCM RBR-ID"
author: "Robert Warneford-Thomson"
date: "7/13/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Import RBR-ID data
```{r}
library(gdata)
installXLSXsupport()
Prot_table <-read.xls(xls = "Scm peptides - only good replicates.xlsx", sheet = 1)
View(Prot_table)
```



## Sanitize Sample names + Add description
```{r}
samples <-c("no4su_01","no4su_02","no4su0.1x_01", "no4su0.1x_02","4su_01","4su_02","4su0.1x_01","4su_0.1x_02")
colnames(Prot_table)[8:15] <- samples
Prot_table[,8:15] <- as.numeric(unlist(Prot_table[,8:15]))
Prot_table <- cbind(Pept_ID = c(1:nrow(Prot_table)), Prot_table)
```

## normalize peptide intensity relative to total intensity
```{r normalize}
# Divide data by Sum of intensities
Norm_data <-sweep(Prot_table[,9:16], 2, colSums(Prot_table[9:16], na.rm = T), FUN = "/")

Prot_table <- cbind(Prot_table, Norm_data)
colnames(Prot_table)[18:25] <- paste0(samples,"_Norm")

```
## Calculate Average/Log-fold change
``` {r average}

#Compute averages of technical replicates
Avgs <- as.data.frame(lapply(c(18,20,22,24), function(x) {apply(Prot_table[,c(x,x+1)], 1, function(x) {mean(x,na.rm = TRUE)})}))
colnames(Avgs)<- c("no4sU1x_mean", "no4sU0.1x_mean", "4su1x_mean", "4su0.1x_mean")

Prot_table <- cbind(Prot_table, Avgs)
ncol(Prot_table)
# Calculate Samples negative log2-fold change
Prot_table$Log2fold_1x <- log2(Prot_table[,28]/Prot_table[,26])
Prot_table$Log2fold_0.1x <- log2(Prot_table[,29]/Prot_table[,27])

Prot_table$Log2fold_1x[is.infinite(Prot_table$Log2fold_1x) | is.nan(Prot_table$Log2fold_1x)] <- NA
Prot_table$Log2fold_0.1x[is.infinite(Prot_table$Log2fold_0.1x) | is.nan(Prot_table$Log2fold_0.1x)] <- NA
```

## Process data and calculate RBR-ID score
``` {r Analysis}

# Calculate p-value from two-sided t-test
Prot_table$p.value_1x <- apply(Prot_table[, c( "no4su_01_Norm","no4su_02_Norm","4su_01_Norm", "4su_02_Norm")], 1, function(x) {if (all(x==0)) {return(NA)} else { t.test( x[1:2], x[3:4],alternative = "two.sided")$p.value}})

Prot_table$p.value_0.1x <- apply(Prot_table[, c( "no4su0.1x_01_Norm","no4su0.1x_02_Norm", "4su0.1x_01_Norm", "4su_0.1x_02_Norm")], 1, function(x) {if (all(x == 0)) {return(NA)} else { t.test( x[1:2], x[3:4],alternative = "two.sided")$p.value}})

# RBR-ID score
Prot_table$score_1x <- log(Prot_table$p.value_1x)*Prot_table$Log2fold_1x

Prot_table$score_0.1x <- log(Prot_table$p.value_0.1x)*Prot_table$Log2fold_0.1x

```

## Calculate 'Internal' contaminant-to-signal ratio
  These include proteins that were purposefully added to the samples during the experiment (e.g. Protein G from beads, rabbit IgG).
  External contaminants are those that are commonly found in mass spectrometry runs
  
``` {r 'Add in'}

#Label contaminant types
Addin_ID <- c("P19909", "P01870","P01826", "P01840","P01687")
temp <- lapply(Addin_ID, function(x) {grep(pattern = paste0("^.+", x,".+$"), Prot_table$Proteins, value = FALSE)})
temp <- unlist(temp)

Prot_table[,"Contaminant_type"] <- "Signal"
Prot_table[temp,"Contaminant_type"] <- "Internal"
Prot_table$Contaminant_type[(Prot_table$Potential.contaminant=="+") & (Prot_table$Contaminant_type != "Internal")] <- "External"


library(ggplot2)
library(reshape2)

## Calcuate proportion of Contaminants to total peptide intensities
## Calculate total contaminant-to-signal ratio
Contam_prop <- data.frame(ID = names(Prot_table)[25:28], 
                          Internal = colSums(Prot_table[which(Prot_table$Contaminant_type == "Internal"),c(25:28)]),
                          External = colSums(Prot_table[which(Prot_table$Contaminant_type == "External"),c(25:28)]),
                          Signal = colSums(Prot_table[which(Prot_table$Contaminant_type == "Signal"),c(25:28)]))
rownames(Contam_prop)

    #Add an id variable for the filled regions
    
    datm <- melt(cbind(Prot_table[,c(25:28)], Contaminant = Prot_table$Contaminant_type), id.vars = c('Contaminant'))

library(scales)
ggplot(datm,aes(x = variable, y = value, fill = Contaminant)) + 
    geom_bar(position = "fill",stat = "identity") + 
    scale_y_continuous(labels = percent_format()) +
    coord_flip() +
    scale_fill_discrete(guide = guide_legend(title = "Signal Type")) +
    labs(x = "Treatment", y = "Percent of Total", title = "RWT-46 Proportion of Signal to total intensity")
    
```
